\section{Conclusion}

The purpose of this requirement analysis was to get a good grasp how we should move forward with the design pattern and identify key aspects for the online marketplace FireSale!. Our team decided it was in the project's best interest for us to meet up on campus to discuss and plan our schedule for the coming days and got to work right away on Monday morning. \\


\noindent A plan was formulated to conduct two types of interviews, first off a design interview to get a good idea of what our users needs and expectations are for the functionality and highlights of the website should be. It was clear that a good search function with a possible filter system, ratings for sellers and buyers however with sellers ratings being more important than buyers ratings are key aspects for such a website. We introduced a potential solution to issues for disputes that may occur during sales with FireSale! offering a third party mediator to settle any disputes so that our customers have the possibility to avoid the hassle of handling those themselves and we received positive feedback to this idea but most interviewees would prefer direct communication so this idea is a possible addition later on.\\


\noindent Second round of interviews were wireframe interviews to check our interpretation of the design with users and see if usability goals were up to standard. These interviews showed a obvious design flaw with our login system where users were unable to move forward after entering their username and password, future design will include a button to move forward. The interviews concluded that users speed, accuracy and success was quite good and feedback was positive for the most part. With this result the team is happy to move forward to the next design phase. 