\section{Usability tests - abstract}
On the 27th of April, we conducted a series of tests on 4 potential users of the platform. The tests were all conducted at Reykjavík university and the goal was to test our wireframe for any obvious error or UX flaws. Testers were all students of the university.
The test consisted of 10 items, that went through some functionality of website. Each item of the test took somewhere between 8 and 80 seconds to complete.\\\\
The test captured the process of registering, logging in / logging out, search using the search bar, search using the category tree, updating the profile, selecting a product, placing a bid, creating an item posting, accepting a bid as a seller and finishing the checkout process. \\\\
In our tests we had an accuracy rating of 99\% and each item took 22 seconds to complete on average. One of our task was flawed since the wireframe does not include a button to complete the login process. This will be fixed in our final design. Another key part of the UI, the condition of the item, was also missing and finally our checkout process was missing the wireframe for selecting delivery, which was added to our wireframes after the fact.\\\\
Overall, our testers felt the design to be intuitive and easy to use but had some opinions regarding some of the design choices. One user felt that hiding important actions, such as viewing bids and active sales should not be hidden behind a dropdown and two felt the placement and wording of register item to be awkward. Some minor grievances were also mentioned but are more relevant for the final design rather then the usability of the website. \\\\
A complete overview of the test can be found in the supplementary material. 