\section{Wireframes and prototype interviews}
To gather information about the requirements, we conducted several interviews with potential user of FireSale. The data used for our interview analysis can be found in the supplementary materials included with this report.

Building from the interview analysis, benchmarking and other factors, we built a wireframe containing a rough draft of how FireSale could look like. That wireframe was then used with potential users to conduct simple usability tests, the purpose of which was to spot any obvious design errors. 

Interviews were all conducted in Icelandic, but for the purpose of this report, the questions were translated to English. The original list can also be found within the supplementary materials included with this report.
\subsection{Questionnaire for the requirement analysis}
\begin{itemize}
    \item Have you ever used a digital marketplace before? (Craigslist, Bland, Facebook marketplace, Ebay)
    \subitem If yes, for what purpose
    \subitem if no, Why?
    \item Which one of the marketplaces, listed in the previous question did you use?
    \subitem If the marketplace you used was not listed, which please mention its name.
    \item When browsing online marketplaces, what is the first thing you would like to see.
    \item When viewing item details, what information is most important to you?
    \item Have you ever had any issues with selling a product using an online marketplace?
    \subitem if yes, tell us about that experience.
    \item Have you ever had any issues with buying a product using an online marketplace.
    \subitem if yes, tell us about that experience.
    \item Do you think you would be more likely to buy a product on an online marketplace, or sell a product?
    \item What product types would you prefer to buy on an online marketplace.
    \item What product types would you prefer to sell on an online marketplace
    \item Would you like to have a selection of delivery/hand-off options
    \subitem if yes, what options do you wish to have
    \item Do you consider the sellers rating to be important when you buy a product
    \item Do you consider the buyers rating to be important when selling a product
    \item If you ran into a problem with a product that you bought, how would you like to handle the problem. Would you try to contact the seller directly or do you want the option of sending the dispute to a third party for a fee.
    \item What functionality do you want to have on an online marketplace
    \item What is your profession
    \item How old are you
    \item What are your hobbies
    \item What is your gender
\end{itemize}
\subsection{Interview analysis}